Figure supplements

### 2023-01-08 text/Manuscript.Rmd
edit text

![**Figure 1. Identification of NOS-expressing interneurons (INNOS) within the cPRC circuit.** **(A)** SEM image of a 3-day-old Platynereis larva. **(B and C)** Five types of neurons (cPRC, INNOS, INRGWa, Ser-h1 and MC) in the cPRC circuit reconstructed in the whole-body transmission electron microscopy (ssTEM) dataset of a 3-day-old larva. Ciliated cells labelled with (B) are shown in grey. The INNOS on the ventral side labelled with (C) are shown in purple. Axons and dendrites appear as lines and cell body positions are represented by spheres. **(D)** Expression analysis of the NOS gene (magenta) using in situ HCR. Anterior view of the larva at 2-day-old. Co-stained image using acetylated α-tubulin antibody (acTub: green). **(E)** Immunostaining with anti-HA antibody against HA tagged palmitoylated-tdTomato expressed under the upstream of the start site of NOS (NOSp::palmi-3xHA: magenta). Co-staining with acetylated α-tubulin antibody as marker for cilia of cPRC and axonal scaffold (acTub: green). Views of larvae at 3-day-old from the anterior side. **(F)** Wiring diagram of the cPRC circuit. Hexagons and arrows represent neuron groups and their synaptic connections, respectively. Numbers inside hexagons indicate the number of neurons grouped in each node. Interactions with less than five synapses were filtered out in this display. Arrow line thickness (synapse weight) is equal to the common logarithm of the number of synapses (scale is shown on the bottom left of the panel).](../figures/Fig1.png){width="100%"}

@@

![**Figure 2. Larvae with inhibited NOS have shorter ciliary arrest times and a delayed response to UV-avoidance.** (A) Vertical swimming in larvae treated with NOS inhibitors, L-NAME at 3-day-old stimulated with UV (395 nm) light from side, blue (488 nm) light from top and UV (395 nm) light from top. The data are shown in 30 s bins. (B) Top: The domain and Exon/Intron structure of NOS. Bottom: Close-up region showing the genomic locus of NOS gene and the wild-type sequence (WT) targeted by CRISPR/Cas9. The generated mutants (NOSΔ11, NOSΔ23) are also shown. Pink indicates target sites. Gray shows PAM sequences, red shows stop codons. (C and D) Vertical swimming in wild-type (WT) and mutant (NOSΔ11 and NOSΔ23) larvae at 2-day-old (C) and 3-day-old (D) stimulated with UV (395 nm) light from side, blue (488 nm) light from top and UV (395 nm) light from top. The data are shown in 30 s bins. (E and F) Overlaid trajectories for WT (left, n=20) and NOS mutant (right, n=31) 3-day-old larvae. Grey shows the trajectories before UV stimulation and purple shows the trajectories after UV stimulation. (E) The temporal changes in the vertical position of the WT and mutant larvae before and after UV stimulation are shown. The starting points of each larval trajectory are set to 0.(F) The temporal changes in the distance traveled of the WT and mutant larvae before and after UV stimulation are shown.(E and F) After UV stimulation is indicated by purple squares.](../figures/Fig2.png){width="100%"}

@@

![**Figure 3. NO produced by UV stimulation to cPRCs induces a depolarising response in cPRC.** (A) A NO-positive cell visualised by DAF-FM is shown (dashline). The white dashed line indicates the outer frame of the larva. All subsequent images are of 2-day-old larvae. (B) Intensity changes before and during 405 nm light stimulation in a cell visualised by DAF-FM. (C) The intensity of DAF-FM changes over time when cPRC (green) and other cells (NC) (gray) are stimulated with UV/violet (405 nm) light. Purple squares indicate the timing of 405 nm light stimulation, the transparent lines show the optical responses to individual intensities, each intensities are normalized (ΔF/F0) and the dark trace lines and the shaded bands show the mean value and the standard error range of the mean. (D and E) Changes over time in GCaMP6s intensities in cPRC when stimulated with UV in WT (dark yellow) and NOS mutant (D: NOSΔ11/Δ11, E: NOSΔ23/Δ23) (light yellow) larvae.](../figures/Fig3.png){width="100%"}

@@

![**Figure 4. cPRC-specific expression of NIT-GC1 localises in close proximity to NOS in the ANS region.** (A) Expression analysis of the NIT-GC1 gene (magenta) using in situ HCR. White arrowheads indicate cells expressing NIT-GC1.Co-staining image using acetylated α-tubulin antibody (ac α-tub: green). (B) Co-expression analysis image of the c-opsin1 gene (green). Black arrowheads indicate cells expressing c-opsin1 differently from cPRC. (C and D) Localisation analysis using NIT-GC1 and NIT-GC2 antibodies. Green shows co-staining with acetylated α-tubulin antibody (ac α-tub).(E-G) Changes over time in GCaMP6s intensities in cPRC when stimulated with UV in control (non-injection) and NIT-GC1 and NIT-GC2 knockdown by morpholino (MO1 and 2) larvae.(H) The domain structure of NIT-GC1. Grey squares indicate the transmembrane domain.(I) A schematic of the NIT-GC1 assay; COS7 cells were used to express NIT-GC1 and the cGMP indicator Green cGull, and the NO donor SNAP and DMSO as control. Green cGull shows cGMP-dependent green fluorescence. (J-M) The intensity changes in cGMP fluorescence over time for the four conditions are shown. Gray traces show the optical responses to individual intensities (n \> 6). The individual intensities are normalized (ΔF/F0). The dark line shows the mean value and the band the standard error range of the mean. The respective solution was acted on 2 min after the start of imaging (grey bars).](../figures/Fig4.png){width="100%"}

>>>>

![**Figure 1. Identification of NOS-expressing interneurons (INNOS) within the cPRC circuit.** **(A)** SEM image of a 3-day-old Platynereis larva. **(B, C)** Five types of neurons (cPRC, INNOS, INRGWa, Ser-h1 and MC) in the cPRC circuit reconstructed in the whole-body transmission electron microscopy (ssTEM) dataset of a 3-day-old larva. Ciliated cells labelled with (B) are shown in grey. The INNOS on the ventral side labelled with (C) are shown in purple. Axons and dendrites appear as lines and cell body positions are represented by spheres. **(D)** Expression analysis of the NOS gene (magenta) using in situ HCR. Anterior view of the larva at 2-day-old. Co-stained image using acetylated α-tubulin antibody (acTub: green). **(E)** Immunostaining with anti-HA antibody against HA tagged palmitoylated-tdTomato expressed under the upstream of the start site of NOS (NOSp::palmi-3xHA: magenta). Co-staining with acetylated α-tubulin antibody as marker for cilia of cPRC and axonal scaffold (acTub: green). Views of larvae at 3-day-old from the anterior side. Insert: One of the reconstracted INNOS is shown from the anterior side. **(F)** Wiring diagram of the cPRC circuit. Hexagons and arrows represent cell groups and their synaptic connections, respectively. Numbers inside hexagons indicate the number of cells grouped in each node. Arrow line thickness (synapse weight) is equal to the number of synapses.](../figures/Fig1.png){width="100%"}

@@

![**Figure 2. NO produced by UV stimulation to cPRCs.** **(A)** A NO-positive cell visualised by DAF-FM (green) is shown (dashline). The white line indicates the outer frame of the larva. All subsequent images are of 2-day-old larvae. **(B)** Intensity changes before (upper) and during 405 nm light stimulation (lower) in a cell visualised by DAF-FM. **(C)** The intensity of DAF-FM changes over time when cPRC (green) and other cells (ctr: gray) are stimulated with UV/violet (405 nm) light. Purple squares indicate the timing of 405 nm light stimulation, the transparent lines show the optical responses to individual intensities, each intensities are normalized (ΔF/F0) and the dark trace lines and the shaded bands show the mean value and the standard error range of the mean.](../figures/Fig2.png){width="100%"}

@@

![**Figure 3. Larvae with inhibited NOS have a delayed response to UV-avoidance.** **(A)** Top: The domain and Exon/Intron structure of NOS. Bottom: Close-up region showing the genomic locus of NOS gene and the wild-type sequence (WT) targeted by CRISPR/Cas9. The generated mutants (NOSΔ11, NOSΔ23) are also shown. Pink indicates target sites. Gray shows PAM sequences, red shows stop codons. **(B)** Overlaid trajectories for WT (left, n=20) and NOS mutant (right, n=31) 3-day-old larvae. Grey shows the trajectories before UV stimulation and purple shows the trajectories after UV stimulation. **(C)** The temporal changes in the vertical position of the WT and mutant larvae before and after UV stimulation are shown. The starting points of each larval trajectory are set to 0. After UV stimulation is indicated by purple squares. **(D)** Vertical swimming in wild-type (WT) and mutant (NOSΔ11 and NOSΔ23) larvae at 3-day-old stimulated with UV (395 nm) light from side, blue (488 nm) light from top and UV (395 nm) light from top. The data are shown in 30 s bins. **(E)** Vertical swimming in larvae treated with NOS inhibitors, L-NAME at 3-day-old stimulated with UV (395 nm) light from side, blue (488 nm) light from top and UV (395 nm) light from top. The data are shown in 30 s bins. .](../figures/Fig3.png){width="100%"}

@@

![**Figure 4. cPRC-specific expression of NIT-GC1 localises in close proximity to NOS in the ANS region.** (D and E) Changes over time in GCaMP6s intensities in cPRC when stimulated with UV in WT (dark yellow) and NOS mutant (D: NOSΔ11/Δ11, E: NOSΔ23/Δ23) (light yellow) larvae. (A) Expression analysis of the NIT-GC1 gene (magenta) using in situ HCR. White arrowheads indicate cells expressing NIT-GC1.Co-staining image using acetylated α-tubulin antibody (ac α-tub: green). (B) Co-expression analysis image of the c-opsin1 gene (green). Black arrowheads indicate cells expressing c-opsin1 differently from cPRC. (C and D) Localisation analysis using NIT-GC1 and NIT-GC2 antibodies. Green shows co-staining with acetylated α-tubulin antibody (ac α-tub).(E-G) Changes over time in GCaMP6s intensities in cPRC when stimulated with UV in control (non-injection) and NIT-GC1 and NIT-GC2 knockdown by morpholino (MO1 and 2) larvae.(H) The domain structure of NIT-GC1. Grey squares indicate the transmembrane domain.(I) A schematic of the NIT-GC1 assay; COS7 cells were used to express NIT-GC1 and the cGMP indicator Green cGull, and the NO donor SNAP and DMSO as control. Green cGull shows cGMP-dependent green fluorescence. (J-M) The intensity changes in cGMP fluorescence over time for the four conditions are shown. Gray traces show the optical responses to individual intensities (n \> 6). The individual intensities are normalized (ΔF/F0). The dark line shows the mean value and the band the standard error range of the mean. The respective solution was acted on 2 min after the start of imaging (grey bars).](../figures/Fig4.png){width="100%"}

### 2023-01-08 text/Supplements.Rmd
edit a part of manuscripts
edit text

>>>>

![**Figure 1---figure supplement 2.** Expression analysis of the NOS gene (magenta) using in situ HCR using the larva at 3-day-old in dorsal view (A) and anterior view (B). (B) Insert: showing two NOS cells on each side.](../figures/Fig1_sup2.png){width="100%"}

![**Figure 3---figure supplement 1.** Expression analysis of the NOS gene (magenta) using in situ HCR using the larva at 3-day-old in dorsal view (A) and anterior view (B). (B) Insert: showing two NOS cells on each side.(F) The temporal changes in the distance traveled of the WT and mutant larvae before and after UV stimulation are shown.(E and F) After UV stimulation is indicated by purple.](../figures/Fig3_sup1.png){width="100%"}
